Categorical Predictor Embeddings in Actuarial Modeling

### 2021-03-16 manuscript/manuscript.Rmd

For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
on a line, as in Figure \@ref(fig:num-floors). In the case of `flood_zone`, since we happen to have the luxury of knowing a
priori the meaning of the prefixes, we can plot them separately to see how the model mapped them. (TODO insert chart).
(insert any observations).

@@

@@

To evaluate these baseline models and other models in this paper, we perform 10-fold 
cross validation and compare the 
root mean square error (RMSE) on the predicted and actual paid amounts.
(somehwere we should say we're not doing a kaggle competition here and the performance metrics are really meant
to show that the models aren't complete shit)
(maybe a couple boxplots showing metrics for baseline models)

>>>>

For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
on a line, as in Figure \@ref(fig:num-floors). In the case of `flood_zone`, since we happen to have the luxury of knowing a
priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the model 
mapped them.

@@

```{r flood-zone, echo = FALSE, fig.cap="Flood zone embeddings", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/flood_zone.png")
```

@@

(TODO)
